---
title: "Seat mapping"
author: "Tianze (Steven) Shou"
date: "6/9/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

## What's this for? 

A curated file named `curated_seating_char_shou.csv` needs to be populated with the following columns: 

+ PeriodID (1-5)
+ DayID (1-3)
+ SeatNum (1-29)
+ anon_user_id (i.e., <Stud_xxx>)
+ actual_user_id (i.e., <greenalpaca>)
+ X
+ Y

`PeriodID`, `DayID`, `SeatNum`, and `actual_user_id` had to be manually entered since the data are presented by seating charts drawn by Shamya. This Rmd file takes care of the remaining columns and enter them automatically since I am very lazy. The mapping information is drawn from `IDmapping_WVW.csv` and `seating_chart_x_y_shou.csv` 

## Reading in necessary data 

```{r}
IDmapping_df = read_csv("IDmapping_WVW_copy.csv") 
seat_coor_df = read_csv("seating_chart_x_y_shou.csv")
output_df = read_csv("curated_seating_chart_shou.csv")
```

## Mapping seat number to X and Y coordinates 

Seat number to X, Y coordinates mapping is in `seating_chart_x_y_shou.csv` file. 

```{r}
output_length = length(output_df$SeatNum)
X = rep(NA, output_length)
Y = rep(NA, output_length)
for(i in 1:output_length) { 
  # matching seat number in the output df with the seat# of seat_coor_df
  # i is for output_df indexing, index is for seat_coor_df
  index = which(seat_coor_df$`seat#` == output_df$SeatNum[i]) 
  X[i] = seat_coor_df$X[index]
  Y[i] = seat_coor_df$Y[index] 
}

output_df$X = X 
output_df$Y = Y

```


## Mapping actual user ID's to anonymous user ID's 

Actual user ID to anonymous user ID mapping is in `IDmapping_WVW.csv` file 

```{r}
output_length = length(output_df$SeatNum)
anon_user_id = rep(NA, output_length)
for(i in 1:output_length) { 
  # matching actual_user_id in the output df with the actual_user_id# of IDmapping_df
  # i is for output_df indexing, index is for IDmapping_df
  index = which(IDmapping_df$actual_user_id == output_df$actual_user_id[i])
  
  # if there is not matching actual_user_id in IDmapping dataframe 
  if(length(IDmapping_df$anon_user_id[index]) == 0) {
    # assign the corresponding anon id value to be NA 
    # since its anon id is not found
    corr_anon_id = NA
  }
  else {
    corr_anon_id = IDmapping_df$anon_user_id[index]
  }
  
  #cat("Actual ID is", output_df$actual_user_id[i], "\n")
  #cat("Matched anon ID is", corr_anon_id, "\n\n") 
  anon_user_id[i] = corr_anon_id 
}

# transcribe to the output dataframe 
output_df$anon_user_id = anon_user_id 
```

## Storing output dataframe in a csv file 

```{r}
write_csv(output_df, "student_position_sprint1_shou.csv") 
```





